\section{Introduction and Planning}
\subsection{Introduction}
The database was completely redesigned from previous years in terms of the schema, and how our Python code interfaces with the database.
A highly extendible database wrapper was written in Python, and support for SQLite and Polyhedra was included. The design of this wrapper makes incorporating new database engines - other than SQLite and Polyhedra - extremely easy.
\newline
A layer of abstraction is created to separate the developer from the raw SQL statements, but also allowing controller access to raw SQL statements when no other option is available.
As well as creating a layer of abstraction to aid database development and integration, database interaction also take place behind the scenes, thanks to Python decorators.
\newline
The database will allow a central storage location of sensor and actuator data. Sensor modules write what is being sensor to the database, actuators write their movements to the database. This allows any of the control software to read the database when it requires. 

\subsection{Planning}
The database was designed to have a different table for each sensor and each actuator. This is necessary as different sensor and actuators require different formats to store their data in. Furthermore this initiative design makes it easier for a human to read, which in turn benefits debugging. 
\newline
Initially it was only considered to include sensor data, however after consideration it was decided it would be beneficial to include actuator data as well; such benefits may be using the motor data for odometer and using the arm data to replay previous actions.



